% !TEX root = SystemTemplate.tex

\chapter{Industrial Experience}

\section{Resumes}

%    \includepdf[pages={1}]{report.pdf}  %% example of limited page include

%     \includepdf{resume1.pdf}
%     \includepdf{resume2.pdf}
%     \includepdf{resume3.pdf}

\section{Industrial Experience Reports}

\subsection{Anthony Morast}

% Report

\subsection{}

% Report
\subsubsection{Describe the context from which results are reported: organization, problem domain, projects, produces, processes}
\paragraph{} Code development was done on Linux. It is irrelevant what platform Latex was done on. Our code was developed in the Qt Creator IDE. However it was tested by compiling and running our code from a command prompt window.

\paragraph{}
In our team Benjamin was assigned Product Manager, James Tillma was assinged Project Manager (SCRUM Master), and Anthony Morast was assigned technical lead. This worked out for the most part though it was clear that with different schedules we would not be able to completely adhere to the roles for each position. 

\paragraph{}
On January the 31st 2014 Benjamin Sherman met with the Customer and obtained the project requirements and details.

\paragraph{}
The different schedules of the team members inhibited project coordination and scheduling. Consequently the project consisted of a group effort and the roles where at times rather undefined.

\subsubsection{Describe software technologies and why they are important}
The product developed is capable of grading a program from a student in Computer Science \textit{I}. Normally a professor or teachers assistant can do this by hand but with our product, grading a Computer Science \textit{I} class becomes an easy task that can be done by one person.

\paragraph{} The only cost of using this product is the user of the product must provide test cases in the form of a [filename].tst with a input for a program to be graded and a [filename].ans with the solution for the test case. This may seem like more work but once test cases are developed many students' programs can be graded. This can save the user lots of time and resources by automating part of the grading process.

\paragraph{}
It should be noted that this product is very versatile and should be useful on most any program submitted by a Computer Science \textit{I} student. This is true only when a students program only accepts input from one file or from the command line AND when the students program only outputs to a file called "output.txt".

\subsubsection{Provide effectiveness and efficiency data leading to the assessment of the technologies}
The finished product was tested on the cases provided by the customer. The different cases provided our solution with different directory structure environments and different input and output cases for student source code. This testing of the product has demonstrated its efficiency and effectiveness that is required by the customer.

\subsubsection{Interpret result, explain consequences, draw conclusions}
Our process is wanting in some aspects of the Agile process which in turn slightly slowed down the development process.

\subsubsection{Discuss limitations of the results and conclusions}
The limiting constraints of our product require that is used on a Linux system and that the user must manually provide all the test cases. There is no GUI to facilitate this process.


\subsection{James Tillma}

% Report

